Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-19 outputs/paper/paper.qmd
Edits

Sociodemographics:

-   Age Group

-   Gender

-   State

-   German Citizen

-   Marital Status

-   Relationship status, single

-   Religious Affiliation

-   Education

-   Occupation

-   Income

-   Household Size

-   Subjective Social Status

-   Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality

-   Politics: left and right-leaning

-   Politics: affiliated parties

Mate Competition: using a scale of agree or disagree

-   Does the influx of male refugees make it difficult for non-immigrant german men to find female partners

Job Competition: using a scale of agree or disagree

-   The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs

Life Satisfaction: scale of 0-10

-   Satisfaction with life

Encountering Refugees

-   How many KM is the closest refugee reception center from your home \* How many refugees do you believe have settled in your municipality in the last year \* In the last month, how many refugees have you encountered in the following locations

Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree

-   Violence is sometimes the only means that citizens have to get the attention of German politicians \* Attitudes towards Muslims

-   Hostility against refugees justified

-   Politicians should condemn attacks against refugees

-   Racist violence is defensible if it leads to fewer refugees settling in a town

-   Attacks against refugee homes are sometimes necessary to make garner the attention of politicians

-   Refugee integration in Germany

-   German refugees should be entitled to German citizenship

-   The number of refugees should be reduced

-   Refugees are receiving more than non-immigrant Germans

-   Refugees should give up their culture to adopt that of Germany

-   Refugees are good for the economy

-   Refugees increase crime

-   Increased refugees increase the risk of terrorism

-   Will additional refugees in your town increase the influence of Islam (local)

-   Will additional refugees in your town be a challenge for local schools (local)

-   Will additional refugees in your town increase competition for housing (local)

-   Will additional refugees in your town change the way of life in your town (local)

Operational category

-   Experiment lists

-   Treatment lists

-   Outcome lists

-   Waves: out of 4

@@

# Ethical Implications

@@

s_tot %>% 
  ggplot(aes(x=terc, y=mean, group=grp, fill=grp)) +
  geom_col(position = "dodge")+
  labs(x="Terciles of Excess Male Rate", fill = "Group") +
  labs(y = wrapper("Proportion perceiving refugees as mate competition", width = 30)) +
  theme_minimal() +
  theme(legend.position="bottom") +
  theme(text=element_text(size=11, family="serif")) +
  ggtitle(wrapper("Nearly half of mating-aged men living in excess male areas perceive refugees as a threat to finding a partner", width =60)) +
  theme(plot.title = element_text(face = "bold"))
```

@@

s_stmt <- survey_data[survey_data$wave == 2,]
s_stmt <- select(s_stmt, c(only_means, message, prevent, condemn, justified, list, treatment_list))

s_stmt$meansp <- ifelse(s_stmt$only_means >= 3, 1, 0)
s_stmt$msgp <- ifelse(s_stmt$message >= 3, 1, 0)
s_stmt$prevp <- ifelse(s_stmt$prevent >= 3, 1, 0)
s_stmt$justp <- ifelse(s_stmt$justified >= 3, 1, 0)

s_stmtmeans <- s_stmt %>% 
  na.omit(meansp)
meansp <- mean(s_stmt$meansp)
msgp <- mean(s_stmt$msgp)
prevp <- mean(s_stmt$prevp)
justp <- mean(s_stmt$justp)

@@

```{r}
#| label: tbl-mate
#| fig-cap: "look at dat"
#| echo: false
#| message: false
#| warning: false
#| include: false

>>>>

Sociodemographics: \* Age Group \* Gender \* State \* German Citizen \* Marital Status \* Relationship status, single \* Religious Affiliation \* Education \* Occupation \* Income \* Household Size \* Subjective Social Status \* Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality \* Politics: left and right-leaning \* Politics: affiliated parties

Mate Competition: using a scale of agree or disagree \* Does the influx of male refugees make it difficult for non-immigrant german men to find female partners

Job Competition: using a scale of agree or disagree\
\* The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs

Life Satisfaction: scale of 0-10 \* Satisfaction with life

Encountering Refugees \* How many KM is the closest refugee reception center from your home \* How many refugees do you believe have settled in your municipality in the last year \* In the last month, how many refugees have you encountered in the following locations

Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree \* Violence is sometimes the only means that citizens have to get the attention of German politicians \* Attitudes towards Muslims \* Hostility against refugees justified \* Politicians should condemn attacks against refugees \* Racist violence is defensible if it leads to fewer refugees settling in a town \* Attacks against refugee homes are sometimes necessary to make garner the attention of politicians \* Refugee integration in Germany \* German refugees should be entitled to German citizenship \* The number of refugees should be reduced \* Refugees are receiving more than non-immigrant Germans \* Refugees should give up their culture to adopt that of Germany \* Refugees are good for the economy \* Refugees increase crime \* Increased refugees increase the risk of terrorism \* Will additional refugees in your town increase the influence of Islam (local) \* Will additional refugees in your town be a challenge for local schools (local) \* Will additional refugees in your town increase competition for housing (local) \* Will additional refugees in your town change the way of life in your town (local)

Operational category \* Experiement lists \* Treatement lists \* Outcome lists \* Waves: out of 4

@@

# \## Ethical Implications

@@

s_tot %>% 
  ggplot(aes(x=terc, y=mean, group=grp, fill=grp)) +
  geom_col(position = "dodge")+
  labs(x="Terciles of Excess Male Rate", fill = "Group") +
  labs(y = wrapper("Proportion perceiving refugees as mate competition", width = 30)) +
  theme_minimal() +
  theme(legend.position="bottom") +
  theme(text=element_text(size=11, family="serif")) +
  ggtitle(wrapper("Nearly half of mating-aged men living in excess male areas perceive refugees as a threat to finding a partner", width =70)) +
  theme(plot.title = element_text(face = "bold"))
```

@@

survey_w2 <- survey_data[survey_data$wave == 2,]

@@

```{r}
#| label: tbl-mate
#| fig-cap: "look at dat"
#| echo: false
#| message: false
#| warning: false
